%-----------------------------------------
% Adrian Maceiras
% Resumé
%
% URL: http://github.com/geota/resume
% Original template by: Xavier Danaux
% This document is covered under the Creative Commons Attribution 3.0 Unported License
%-----------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt,letterpaper,final]{moderncv}
\usepackage{fontspec}
\moderncvtheme[burntorange]{classic}

% DOCUMENT LAYOUT
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2cm}
\AtBeginDocument{\recomputelengths}
% FONTS
\usepackage[utf8]{inputenc}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

% Remove % to set to different fonts
%\setromanfont [Ligatures={Common},Numbers={OldStyle}]{Adobe Caslon Pro}
%\setmonofont[Scale=0.8]{Monaco} 

% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}}

% ---- MARGIN YEARS
%\newcommand{\years}[1]{\marginpar{\scriptsize #1}}


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR


% Personal Information 
\firstname{Adrian}
\familyname{Maceiras}
\address{3906 Carmel Dr.}{Austin, TX 78721}
\mobile{(512) 289-9189}
\email{amac425@utexas.edu}
\homepage{https://github.com/geota}
%

%\title{Adrian Maceiras' Resume}

\nopagenumbers{}

\begin{document}
\makecvtitle
\section{Education}
\cventry{2011--2013 (expected)}{Computer Science \& Geography, University of Texas}{Austin, TX}{}{}{ CS GPA: 4.0, Overall GPA: 3.1, LSAT: 177 - 99.8 percentile.}
\cvline{2005--2009} {Bachelor of Arts in Geography.}
\cvline{2005--2009}{University of Texas Scholarship.}
\cvline{2005}{National Hispanic Merit Scholarship}
\cvline{2011}{Northwestern University Law School Scholarship - declined.}
\cvline{2011}{Sarah T. Hughes Diversity Scholarship - declined.}
\section{Computer Skills} 
  \cvline{Languages:}{Java, C++, PHP, Javascript, Ruby}
  \cvline{Functional Knowledge:}{Python, Rails, MongoDB, SQL, SOAP/REST, jQuery, HTML5, CSS3,  Doxygen}
\section{Experience} 
  \cventry{November 2012--Present}{Skynet Developer Intern}{SFCG}{Austin, TX}{}{
    \begin{itemize}
      \item Implemented numerous CRUD web applications for customers' Oracle CRM implementations.
      \item Implemented an internally used Google Maps API Marker Manager library. 
      \item Extended the Skynet web layer to support additional SOAP operations.
      \item Spearheaded effort to use git and Bitbucket for SCM.
    \end{itemize}
  }
  \cventry{August 2006 --\\March 2012}{Admissions Assistant}{Austin Community College}{}{}{
    \begin{itemize}
      \item Assisted students in issues pertaining to admissions, registration, and access to their educational records.
      \item Assisted in design phase for the TREX electronic transcript submission system. 
    \end{itemize}
  }
  \cventry{March 2010 --\\October 2010}{Intern}{David Kallus Attorney at Law}{The Woodlands, TX}{}{
    \begin{itemize}
      \item Drafted settlement agreements, pleadings, and motions.
      \item Conducted legal research using WestLaw.
      \item Organized and categorized documents acquired through pre-trial discovery.
    \end{itemize}
 }
\section{Completed Courses}
\cvlistdoubleitem{CS429 Computer Org. and Architecture}{CS439 Operating Systems}
\cvlistdoubleitem {CS71P Object-Oriented Programming}{CS345 Programming Languages}
\cvlistdoubleitem{CS314 Data Structures}{CS361 Intro to Computer Security}
\section{Other}
  \cvlistitem{Contributor to mongo-tools - see \url{https://github.com/brandonblack/mongo-tools}}
  \cvlistitem{Simple stock portfolio monitor - see \url{https://github.com/geota/pystocktracker}}
  \cvlistitem{Facebook Open Source Curriculum Hackathon participant.}
  \cvlistitem{LSAT Tutor.}
\end{document}

